\textbf{Computational Fuzzy Extractors}

### 2013-05-18 trunk/CompFuzzExt.tex
Minor revisions from proof reading

%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and traditionally are defined as information-theoretic objects.  The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.  In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$. 
A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.  Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful.

@@

\paragraph {Our Negative Results}
We first study (in  \secref{sec:impossCompSecSketch}) whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called \emph{secure sketch}.  A secure sketch is a one-round information reconciliation protocol: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.  The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.  This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors produce random strings from strings with conditional min-entropy. We call this the \emph{sketch-and-extract} construction.

@@

\begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:fuzzy extractor}
An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability at least $1-\delta$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

@@

%In \secref{sec:impossCompSecSketch} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch? It's not obvious from the way this is written.} \lnote{can we just have a single definition --- the one below --- instead of two?}
%\begin{definition}
%We say that pair of procedures $(\sketch, \rec)$ is $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$ is an \emph{approximately correct secure sketch} if \defref{def:secure sketch} holds with correctness replaced with the following property, $\forall w, w'$ such that $\dis(w, w')\leq t$:
%\[
%\Pr[\rec(w', \sketch(w)) = w]\geq 1-\epsilon.
%\] where the probability is taken over the coins of \sketch and \rec.
%\end{definition}
\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ set $P=(\sketch(w), x), R=\ext(w;x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction.  In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.  We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
\label{sec:imp unp sketch}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  However, HILL entropy is a strong notion.  In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.  We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (our relaxation is analogous to relaxed HILL entropy described in the previous section).

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
Let  $(W, S)$ be a pair of random variables. We say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
\[
\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
.\]
\end{definition}

We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-
hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
Note this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
\emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).

@@

In this section we describe our main construction.  In this section, we consider only a uniform source $W$; we consider other distributions in \secref{sec:LWE block fixing sources}.  Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \secref{sec:time main construction}).

@@

Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$. Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
%The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
%We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):

\begin{proposition} 
\label{assume:entropy LWE}
Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\alpha$ be the discretized Gaussian distribution with variance $(\alpha q)^2/2\pi$.  If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure for $\epsilon = \ngl(n)$ and $s_{sec} = \poly(n)$.  That is, $\delta^{\mathcal{D}_{s_{sec}}}(\vA, \vA X+E ), (\vA, U_{m\log q}))\leq \epsilon$.

@@

\subsection{Efficiency of \consref{cons:informal construction}}
\label{sec:time main construction}
%\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
\consref{cons:informal construction} is only useful if $\decode_t$ can be efficiently implemented.  We need a decoding algorithm for a random linear code with $t$ errors that runs in polynomial time.  We present a simple $\decode_t$.  Replacing our algorithm  with a state of the art algorithm will only increase our correcting capability and improve \consref{cons:informal construction}.

\begin{construction}
\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
\begin{enumerate}
\item Input $\vA , B = \vA X + W - W'$
\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
\item Restrict $\vA, B$ to rows $i_1,...,i_{2n}$, denote this as $\vA_{i_1,...,i_{2n}}, B_{i_1,...,i_{2n}}$.
\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
If no such rows exist go to step (2).
\item Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  If $B- AX'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $X'$.
\end{enumerate}
\end{construction}

$\decode_t$ is an efficient decoding procedure when $t$ is small enough.  We need $t$ to be small enough for none of the selected rows to have errors with probability at least $\frac{1}{\poly(n)}$. Furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.  The second condition is to ensure that there are few false positives in step (5).  This condition is satisfied for $t = O(\frac{m}{n}\log n)$, since random codes have high distance with probability $1-e^{-\Omega(n)}$.  The exact statement is in \corref{cor:code high distance}.  Furthermore, steps (3-5) are computable in time $O(n^3)$.
This is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.  We consider the setting where the running time of $\decode_t$ grows with $t$.  $\decode_t$ is efficient as long as $t$ is small enough.  The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d\log n (m/n-2)$]
\label{lem:i t poly time}
Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.  Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(\frac{m}{n}-2)$.  Then $\decode_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
\end{lemma}
\textbf{Note:} If we consider the setting where $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3\log n)$.  Our main theorems apply when $t\leq m/n-2$ with slightly better parameters.  We concentrate on the setting $t\leq d\log n(m/n-2)$.  Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.

@@

For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\thref{thm:lossless secure extractor log} shows that a computational fuzzy extractor can be built without incurring any entropy loss.  This is essentially due to $\vA X+W$ looking like a uniformly random point and providing no information about either $X$ or $W$.  
%A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.

@@

The following theorem states the main technical result of this section, which is of potential interest outside our specific setting. The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$,  with security degrading exponentially as symbols are fixed (of course, once $n$ symbols are fixed, no security remains, because there are $n$ linear equations with known error and $n$ unknowns).
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.  Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  The $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(X, Y)$ be a joint distribution such that $\Hav(X | Y)\geq k$ and
\[ 
\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\le \epsilon\, ,
\]  
where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. Let $X_y$ denote the random variable $X|Y=y$.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $w\in\mathcal{M}, z \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $w'\leftarrow \neigh(w, t')$.
\subitem If $\rec(w', z) \neq  w$ output $0$.
\item Output $1$.
\end{enumerate}
 By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
$\delta^D((W, \sketch(W)), (X, Y))\le \epsilon$, we know $\Pr[D(X, Y) = 1]\ge 1-\epsilon-t\delta$.  By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]\ge 1- 2(\epsilon + t\delta)$.

@@

\thref{thm:imp of unp entropy} follows by noting that $Z^n$ can be sampled in time $n\log |Z|$ and neighborhood sampled in time $n\log |Z|$.
\subsection{Proof of \thref{thm:imp of unp entropy}}
\label{sec:proof of imp unp entropy}
Instead of proving the result just for Hamming metric over $Z^n$, we will prove the result for any metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.  We now define this second condition:
\begin{definition}
A metric space space $(\mathcal{M}, \dis)$ is $s_{sam}$-\emph{efficiently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that outputs a uniformly random point in $\mathcal{M}$.
\end{definition}

>>>>

%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and are defined (traditionally) as information-theoretic objects.  The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.  In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$. 
A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.  Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful.

@@

\paragraph {Our Negative Results}
We first study (in  \secref{sec:impossCompSecSketch}) whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called a \emph{secure sketch}.  A secure sketch is a one-round information reconciliation protocol: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.  The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.  This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors produce random strings from strings with conditional min-entropy. We call this the \emph{sketch-and-extract} construction.

@@

\begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:fuzzy extractor}
An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

@@

%In \secref{sec:impossCompSecSketch} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch? It's not obvious from the way this is written.} \lnote{can we just have a single definition --- the one below --- instead of two?}
%\begin{definition}
%We say that pair of procedures $(\sketch, \rec)$ is $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$ is an \emph{approximately correct secure sketch} if \defref{def:secure sketch} holds with correctness replaced with the following property, $\forall w, w'$ such that $\dis(w, w')\leq t$:
%\[
%\Pr[\rec(w', \sketch(w)) = w]\geq 1-\epsilon.
%\] where the probability is taken over the coins of \sketch and \rec.
%\end{definition}
\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction.  In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.  We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
\label{sec:imp unp sketch}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  However, HILL entropy is a strong notion.  In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.  We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (we relax the definition slightly, similarly to the relaxation of HILL entropy described in the previous section).

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
Let  $(W, S)$ be a pair of random variables. We say that $W$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unprlx}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
\[
\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
.\]
\end{definition}

We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unprlx}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
Note this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
\emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).

@@

In this section we describe our main construction.  In this section, we consider only a uniform source $W$; we consider other distributions in \secref{sec:LWE block fixing sources}.  Our construction uses the code-offset construction~\cite{JW99}, \cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \secref{sec:time main construction}).

@@

Denote by $\bar{\Psi}_\rho$ the discretized Gaussian distribution over $\Fq$ with variance $(\rho q)^2/(2\pi)$. Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that for $\rho q >2\sqrt{n}$, when $\chi = \bar{\Psi}_{\rho}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
%The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
%Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
%We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):

\begin{proposition} 
\label{assume:entropy LWE}
Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime and let $\bar{\Psi}_\rho$ be the discretized Gaussian distribution with variance $(\rho q)^2/2\pi$.  Let $\rho \in (0,1)$ with $\rho q > 2\sqrt{n}$.  If GAPSVP and SIVP are hard to approximate~(on lattices of dimension $n$) within polynomial factors for quantum algorithms, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure for $\epsilon = \ngl(n)$ and $s_{sec} = \poly(n)$.  That is, $\delta^{\mathcal{D}_{s_{sec}}}(\vA, \vA X+E ), (\vA, U_{m\log q}))\leq \epsilon$.

@@

\subsection{Efficiency of \consref{cons:informal construction}}
\label{sec:time main construction}
%\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
\consref{cons:informal construction} is only useful if $\decode_t$ can be efficiently implemented.  We need a decoding algorithm for a random linear code with $t$ errors that runs in polynomial time.  We present a simple $\decode_t$.  Replacing our algorithm  with a state of the art algorithm will increase our correcting capability and improve \consref{cons:informal construction}.

\newpage
\begin{construction}
\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
\begin{enumerate}
\item Input $\vA , B = \vA X + W - W'$
\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
\item Restrict $\vA, B$ to rows $i_1,...,i_{2n}$, denote this as $\vA_{i_1,...,i_{2n}}, B_{i_1,...,i_{2n}}$.
\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
If no such rows exist go to step (2).
\item Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  If $B- AX'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $X'$.
\end{enumerate}
\end{construction}

$\decode_t$ is an efficient decoding procedure when $t$ is small enough.  We need $t$ to be small enough for none of the selected rows to have errors with probability at least $\frac{1}{\poly(n)}$. Furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.  The second condition is to ensure that there are few false positives in step (5).

We are concerned with the setting $t = O(\frac{m}{n}\log n)$. Random linear codes have distance at least $t = O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$.  The exact statement is in \corref{cor:code high distance}.  This, with overwhelming probability over the choice of $\vA$ the second condition is satisfied.  Furthermore, steps (3-5) are computable in time $O(n^3)$.
Setting $t = O(\frac{m}{n}\log n)$ is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.  We consider the setting where the running time of $\decode_t$ grows with $t$.  The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d\log n (m/n-2)$]
\label{lem:i t poly time}
Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.  Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(\frac{m}{n}-2)$.  Then $\decode_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $X$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
\end{lemma}
\textbf{Note:} If we consider the setting where $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3\log n)$.  Our main theorems apply when $t\leq m/n-2$ with slightly better parameters.  We concentrate on the setting $t\leq d\log n(m/n-2)$.  Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.

@@

For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\thref{thm:lossless secure extractor log} shows that a computational fuzzy extractor can be built without incurring any entropy loss.  We can essentially think of $\vA X+W$ as an encryption of $X$ that where decryption works from any close $W'$.
%A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.

@@

The following theorem states the main technical result of this section, which is of potential interest outside our specific setting. The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$,  with security degrading exponentially as symbols are fixed (of course, once $n$ symbols are fixed, no security remains, because there are $n$ linear equations with known error and $n$ unknowns).
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.  Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$~(that is, $\Hoo(W) = mb$).  The $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(X, Y)$ be a joint distribution such that $\Hav(X | Y)\geq k$ and
\[ 
\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\le \epsilon\, ,
\]  
where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. 
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $w\in\mathcal{M}, z \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $w'\leftarrow \neigh(w, t')$.
\subitem If $\rec(w', z) \neq  w$ output $0$.
\item Output $1$.
\end{enumerate}
 By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
$\delta^D((W, \sketch(W)), (X, Y))\le \epsilon$, we know $\Pr[D(X, Y) = 1]\ge 1-\epsilon-t\delta$.  Let $X_y$ denote the random variable $X|Y=y$.  By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]\ge 1- 2(\epsilon + t\delta)$.

@@

\subsection{Proof of \thref{thm:imp of unp entropy}}
\label{sec:proof of imp unp entropy}
Instead of proving the result just for Hamming metric over $Z^n$, we will prove the result for any metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.  We now define this second condition:
\begin{definition}
A metric space space $(\mathcal{M}, \dis)$ is $s_{sam}$-\emph{efficiently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that outputs a uniformly random point in $\mathcal{M}$.
\end{definition}
